---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mypackage)
```

Example 1: Multiple Linear Regression
To fit a multiple linear regression model, just input a formula and dataset to the fit function 'mlr'. This produces a list containing the following objects:
* `Estimate`: the estimated coefficients(betahat)
* `Std. Error`: standard error of betahat
* `t value`: Inference: t statistic for H0: beta=0
* `Pr(>|t|)`: Inference: corresponding p-value for H0: beta=0
```{r}
data(mtcars)
attach(mtcars)
mlr(model.matrix(wt ~ mpg + cyl), as.vector(wt))
detach(mtcars)
```
Compare results to base functions:
Test our results to check whether they correspond with output from function from R base:

```{r}
data(mtcars)
attach(mtcars)
m1 <- lm(wt ~ mpg + cyl, data = mtcars)
m2 <- mlr(model.matrix(wt ~ mpg + cyl), as.vector(wt))
sm1 <- summary(m1)
all.equal(m2, sm1$coefficients)
detach(mtcars)
```
Compare speed to base functions:
Compare`mlr()` to `lm()` by using the **bench** package. 
However the output shows that `lm()` function is faster on average.
```{r}
library(bench)
attach(mtcars)
m1 <- lm(wt ~ mpg + cyl, data = mtcars)
m2 <- mlr(model.matrix(wt ~ mpg + cyl), as.vector(wt))
sm1 <- summary(m1)
detach(mtcars)
bench::mark(
  m2, sm1$coefficients
)
```
Example 2: Ftest for Simple Linear Regression under H0: beta1=0
To conduct a Ftest for Simple Linear Regression, just fit function 'Ftest'. This produces a list containing the following objects:
* `Sum Sq`: Regression sum of squares
* `Mean Sq`: SSE/dfR
* `F value`: Inference: F statistic for H0: beta1=0
* `Pr(>F)`: Inference: corresponding p-value for H0: beta1=0
* `R-squared`: reflects fit of model
* `SSE`: Error sum of squares
* `MSE`: SSE/dfE

```{r}
data(mtcars)
attach(mtcars)
Ftest(mpg,wt)
detach(mtcars)
```

Compare results to base functions:
Test our results to check whether they correspond with output from function from R base:
```{r}
data(mtcars)
attach(mtcars)
SeqSS = data.frame(anova(lm(wt ~ mpg)))
Ftest1 <- Ftest(mpg, wt)
m5<-summary(lm(wt~mpg))
Ftest2 <-
  cbind(SeqSS["mpg", "Sum.Sq"], SeqSS["mpg", "Mean.Sq"], SeqSS["mpg", "F.value"],
        SeqSS["mpg", "Pr..F."], m5$r.squared, SeqSS["Residuals", "Sum.Sq"], SeqSS["Residuals", "Mean.Sq"])

all.equal(Ftest1[1:7], Ftest2[1:7])
detach(mtcars)
```
Compare speed to base functions:
Compare`Ftest()` to `anova(lm())` by using the **bench** package. 
However the output shows that the speed of two function are very close on average.
```{r}
library(bench)
data(mtcars)
attach(mtcars)
SeqSS = data.frame(anova(lm(wt ~ mpg)))
Ftest1 <- Ftest(mpg, wt)
m5<-summary(lm(wt~mpg))
Ftest2 <-
  cbind(SeqSS["mpg", "Sum.Sq"], SeqSS["mpg", "Mean.Sq"], SeqSS["mpg", "F.value"],
        SeqSS["mpg", "Pr..F."], m5$r.squared, SeqSS["Residuals", "Sum.Sq"], SeqSS["Residuals", "Mean.Sq"])
bench::mark(Ftest1[1:7], Ftest2[1:7])
detach(mtcars)
```

Example 3: Realize famous KMP algorithm to find times of appearance of x in y, especially for quite long vectors matching(including 'overlap' parts)
```{r}
kmp(c(1,2),c(1,2,1,2,3))
kmp(c(1,1),c(1,1,1,1,1))
```
Compare results to base functions:
Test our results to check whether they correspond with output from function from R base(identical()):
```{r}
match_vec <- function(x, y) {
  m <- 0
  for (i in 1:c(length(y) - length(x) + 1)) {
    if (identical(x, y[i:c(length(x) + i - 1)]) == TRUE) {
      m <- m + 1
    }
  }
  return(m)
}
all.equal(kmp(c(1, 2), rep(c(1, 2), 1000)), match_vec(c(1, 2), rep(c(1, 2), 1000)))
```

Compare speed to base functions:
Compare`kmp()` to `identical()` by using the **bench** package. 
However the output shows that `kmp()` function is much faster on average.
```{r}
library(bench)
match_vec <- function(x, y) {
  m <- 0
  for (i in 1:c(length(y) - length(x) + 1)) {
    if (identical(x, y[i:c(length(x) + i - 1)]) == TRUE) {
      m <- m + 1
    }
  }
  return(m)
}
bench::mark(kmp(c(1, 2), rep(c(1, 2), 100000)), match_vec(c(1, 2), rep(c(1, 2), 100000)))
```


